\ttitle

### 2013-12-11 Chapters/Chapter6/data_gathering.tex
WIP: Chapter 6

\subsection{Indoor stairs}\label{subsec:indoor_stairs}
The last series of activities recorded consist of walking up and down the stairs, indoor.
The stairs are shaped in an semi-circular form, with a small vertical segment on each floor.
The still of \Cref{fig:data_gathering_still_3_descending} illustrates the circular shape of the stairs.
In \Cref{fig:data_gathering_still_3_ascending} the small flat segment is visible.
Between the stairs the subject has walked in a hallway with a $180^{\circ}$ counter-clockwise turn, as shown in \Cref{fig:data_gathering_still_3_walk}.

>>>>

\subsection{Indoor stairs}\label{subsec:indoor_stairs}
The final series of activities recorded consist of walking up and down the stairs, indoor.
The stairs are shaped in an semi-circular form, with a small vertical segment on each floor.
The still of \Cref{fig:data_gathering_still_3_descending} illustrates the circular shape of the stairs.
In \Cref{fig:data_gathering_still_3_ascending} the small flat segment is visible.
Between the stairs the subject walked in a hallway with a $180^{\circ}$ counter-clockwise turn, as shown in \Cref{fig:data_gathering_still_3_walk}.
The recorded sensor data of the performed activities are visible in the plots of \Cref{fig:data_gathering_run_3_rot,fig:data_gathering_run_3_mag,fig:data_gathering_run_3_acc}.
